### 2017-01-10 paper/evaluation.tex
updating RQ3
updated plot from rq3
adjusted table and updated macros

To evaluate the presence of parallelization settings, we considered
the \numMedLong{} subjects from the \longg{} and \medg{} groups
identified in Section~\ref{sec:rqA}. We focused on these two groups
because given that costly test suites exist, we wanted to investigate
if their maintainers are aware of parallelization settings and how
they use these settings (see Section \ref{sec:modes}).  We computed
the frequency of the parallelism modes using a two-steps approach: the
first step (discovery) automatically finds relevant build files (\ie,
\pomf{} files with parallelization settings); the second step
(inspection) consists in a manual inspection to confirm the presence
of parallelism settings in the build file and classify them according
to the parallelism level (see Section \ref{sec:modes}).
Figure~\ref{fig:discovery-step} describes the discovery step: we list
the paths of all build files and filter only the files that contain
any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
\CodeIn{parallel}.  Notice that, for Maven projects, any of these
keywords exist in any possible parallel setting \Fix{cite surefire
doc}. Our first step is complete but is not sound since the line that
matches one of keywords may not represent part of a real setting (\eg,
comments).  We eliminate false-positives in the confirmation step.

@@

\input{codes/discovery}

\begin{table}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccccc}
        \toprule%
        Group  & Build Files & Filtered files & Settings & Subjects \\%
        \midrule%
        Long   & 1613 & 79 & \Fix{X} & \Fix{X}\\%
        Medium & 1240 & 30 & \Fix{X} & \Fix{X}\\%
        \midrule%
        Total  & 2853 & 109 & \Fix{X} & \Fix{X}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{to-be-defined}}
    \label{tab:inspection-table} 
\end{table}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} projects\Jbc{Currently mocked data}}
\end{figure}

>>>>

To evaluate the presence of parallelization settings, we considered
the \numMedLong{} subjects from the \longg{} and \medg{} groups
identified in Section~\ref{sec:rqA}. We focused on these two groups
because given that costly test suites exist, we wanted to investigate
if their maintainers are aware of parallelization settings and how
they use these settings (see Section \ref{sec:modes}).  We computed
the frequency of the parallelism modes using a two-steps approach: the
first step (discovery) automatically finds relevant build files (\ie,
\pomf{} files with parallelization settings); the second step
(inspection) consists in a manual inspection to confirm the presence
of parallelism settings in the build file and classify them according
to the parallelism level (see Section \ref{sec:modes}).
Figure \Fix{removed} describes the discovery step: we list
the paths of all build files and filter only the files that contain
any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
\CodeIn{parallel}.  Notice that, for Maven projects, any of these
keywords exist in any possible parallel setting \Fix{cite surefire
doc}. Our first step is complete but is not sound since the line that
matches one of keywords may not represent part of a real setting (\eg,
comments).  We eliminate false-positives in the confirmation step.

@@

\begin{table}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
                               &                             &  / false-positives &       / total\\%
        \midrule%
        Long   & 1613 & 79/\Fix{z} & \Fix{X}/\numLong{}\\%
        Medium & 1240 & 30/\Fix{y} & 22/\numMed{}\\%
        \midrule%
        Total  & 2853 & 109/\Fix{z+y} & \Fix{w}/\numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{to-be-defined}}
    \label{tab:inspection-table} 
\end{table}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} projects\Jbc{Currently medium and partially
    the long group...}}
\end{figure}
